Scalar on Function Regression \\ with Applications to Near-Infrared Spectography

### 2022-01-07 Presentation/slides.tex
Slides Meeting

% Title page details: 
\title{Scalar on Function Regression}
\author{Jonathan Willnow, Jakob Juergens, Jonghun Baek}
\date{{\color{red}}Presentation Day}

@@

		\begin{itemize}
			\item Near-infrared (NIR) spectroscopy enables fast diagnostics by using the NIR region of the electromagnetic spectrum (2,500–750 nm)
			\item Suited for field-monitoring / on-line analysis and diagnostics of e.g: prediction of octane ratings!
			\item Spectroscopy results in high-dimensional dataset.	
			\item This set of measurements along a continuum can be viewed as set of smooth spectral curves
			\item Regression to determine relationship between octane rating and spectral curves
			\end{itemize}
	\end{frame}

@@

	\begin{frame}{Theory}
		Jonghun
		\begin{itemize}
			\item Random Functions (name square integrable functions)
			\item Motivate continuous stochastic processes (growth curves/electricity consumption/yield curves/stonks)
			\item Use curves to predict a scalar response (show typical dgp)
		\end{itemize}
	\end{frame}

	\begin{frame}{Theory}
		Jonghun
		\begin{itemize}
			\item Basis expansions (b-splines and fourier)
			\item Talk about purposes
			\item Plots and show bias variance tradeoff
		\end{itemize}
	\end{frame}

	\begin{frame}{Random Function}
		Random element is a function $X : \Omega \rightarrow \mathcal{S}$ which is defined on a common probability space $(\Omega, \mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a $\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}.$
		\begin{itemize}
			\item If $\mathcal{S} = \mathbb{R}$ $\rightarrow$ X is a random variable
			\item If $\mathcal{S} = \mathbb{R}^{n}$ $\rightarrow$ X is a random vector
			\item If $\mathcal{S}$ is a space of functions, $X$ is called a \textbf{Random Function}
		\end{itemize}
	\end{frame}

	\begin{frame}{Random Function}
		Let $\mathbb{E}$ be the index set and this can be described as
		$${\{X(t,\omega) : t \in \mathbb{E}, \omega \in \Omega\},}$$
		where $X(t, \cdot)$ is $\mathcal{F}$-measurable function on the sample space $\Omega$.\\
		\begin{itemize}
			\item It can be shortened to $X(t)$ by omitting $\omega$
			\item The function is realized when the $X(t)$ have been observed for every $t \in \mathbb{E}$
		\end{itemize}
	\end{frame}

	\begin{frame}{Square Integrable Function}
		If a function $f$ satisfies:
		$$\int_{0}^{1} \{f(t)\}^{2}dt < \infty$$
		the function $f$ is called \textbf{Square Integrable Function}\\
		and in the set $\mathbb{L}^{2}[0,1]$.
		\begin{itemize}
			\item Without loss of generality, the interval is defined in $[0,1] $
			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
			\item We focus on $\mathbb{L}^{2} [0,1]$ since the domain of our function is on the real line.
		\end{itemize}
	\end{frame}

	\begin{frame}{Square Integrable Function}
		If $f, g \in \mathbb{L}^{2}[0,1]$,
		$$(ab + bg)(t) = af(t) + bg(t), \quad t \in [0,1] and \forall a,b$$
		, where $a$ and $b$ are scalars. (Maybe don't need)\\
		We can additionally define the inner product as follows:
		$$\langle f,g \rangle = \int_{0}^{1} f(t)g(t)dt$$
		\begin{itemize}
			\item Orthogonolality of two different functions
			\item Distance between functions
		\end{itemize}
	\end{frame}

	\begin{frame}{Stochastic Process Perspective}
		Functional data are the sample curves observed from continuous time stochastic precess.\\
		\begin{itemize}
			\item From this perspective, $X(t)$ is a random variable (?)\\
			\item $X(\cdot)$ is a collection of random variables by each time index(?)\\
			\item Realizations of a random function belong in large collection of functions
		\end{itemize}		
	\end{frame}

@@

	\begin{frame}{Basis Expansion}
		\textbf{Basis Expansion} is a linear combination of functions defining a function as described:
		$$X_{i}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad 1\leq i \leq n, \forall t \in E$$
		, where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient.
		\begin{itemize}
			\item To make the function smoother
			\item To replace the original scalar data $X_{n}(t_{jn})$ by a smaller collection of $c_{nm}$
		\end{itemize}		
	\end{frame}

	\begin{frame}{Two Typical Types of Basis Function}
		\textbf{Fourier Basis Function} is written as
		$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\
		\vspace{2\baselineskip}
		\textbf{B-spline Basis Function} is a flexible curve defined by degree and knots. \\
		Each B-spline basis function, $i$-th B-spline basis function of degree $p$, $N_{i,p}(u)$ is defined on Cox-de Boor recursion formula.(Do you think I need to put the formula?)
	\end{frame}

@@

	\begin{frame}{Trade Off between Bias and Variance}
		How do we choose the number $K$ of basis functions?
		\begin{itemize}
			\item The larger $K$, the better fit to the data with also fitting noise
			\item If $K$ is too small, it would miss some significant information that we want to estimate 
		\end{itemize}
	\end{frame}

	\begin{frame}{Trade Off between Bias and Variance}
		\begin{itemize}
			\item $\textbf{Bias}[\hat{x}(t)] = x(t) - E[\hat{x}(t)]$
			\item $\textbf{Var}[\hat{x}(t)] = E[\{\hat{x}(t) - E[x(t)]\}^2]$
			\item $\textbf{MSE}[\hat{x}(t)] = E[\{\hat{x}(t) - x(t)\}]$
			\item $\textbf{MSE}[\hat{x}(t)] = \textbf{Bias}^2[\hat{x}(t)] + \textbf{Var}[\hat{x}(t)]$
		\end{itemize}
		In the sense of that, we need to concentrate on decreasing \textbf{MSE}.
	\end{frame}

@@

	\begin{frame}{Estimation via Basis Representation}
		Assume the following \textbf{Data Generating Process}
		$$Y(\omega) = \alpha + \int_{0}^{1} \beta(s) F(\omega)(s) \mathrm{d}s + \epsilon(\omega)$$
		\begin{itemize}
			\item $Y(\omega)$ and $\epsilon(\omega)$ realize in $\mathbb{R}$ and $F(\omega)$ realizes in $\mathbb{L}^2[0,1]$
		\end{itemize}
		\vspace{0.2cm}

		Assume that we have a data set containing observations each of which is made up of:
		\begin{itemize}
			\item $y_i$: a scalar realization of $Y(\omega)$
			\item $f_i(t)$: a realization of $F(\omega)$
		\end{itemize}

@@

	\begin{frame}{Estimation via Basis Representation}
		Let $\{b_i(t) \: \vert \: i = 1, \dots, \infty\}$ be a basis of $\mathbb{L}^2[0,1]$
		\vspace{0.2cm}

		Then we have the following representation of $\beta(t)$
		$$\beta(t) = \sum_{j = 1}^{\infty} \psi_j b_j(t) = \sum_{j = 1}^{L} \psi_j b_j(t) + \delta(t) \approx \sum_{j = 1}^{L} \psi_j b_j(t)$$
		and we can transform the data generating process into:
		\begin{equation}\notag
			\begin{split}
				Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j = 1}^{\infty} \psi_j  b_j(s)\right) F(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
						  & = \alpha + \sum_{j = 1}^{\infty} \left[\psi_j \textcolor{red}{\int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s}\right] + \epsilon(\omega)	  
			\end{split}
		\end{equation}
	\end{frame}

	\begin{frame}{Estimation via Basis Representation}
		$$Z_j(\omega) = \int_{0}^{1} F(\omega)(s) b_j(s)\mathrm{d}s$$ 
		This is a \textbf{scalar random variable} leading to the following transformation
		$$Y(\omega) = \alpha + \sum_{j = 1}^{\infty} \psi_j Z_j(\omega) + \epsilon(\omega)$$
		Each combination of observation $f_i(t)$ and deterministic basis function $b_j(t)$ effectively gives us a realization of this random variable.
		$$Z_{i,j} = \int_{0}^{1} f_i(s) b_j(s)\mathrm{d}s$$

	\begin{frame}{Estimation via Basis Representation}
		This allows us to write each observation in the data set as
		\begin{itemize}
			\item $y_i$: a scalar realization of $Y$
			\item $\left(Z_{i,j}\right)_{j \in \mathbb{N}}$: a countably infinite sequence of scalars
		\end{itemize}
		\vspace{0.2cm}

		Truncating the functional basis allows us to approximate the data set in the usual multivariate form.
		\begin{itemize}
			\item $y_i$: a scalar realization of $Y$
			\item $\left(Z_{i,1} \: \dots \:  Z_{i,L} \right)'$: a vector of scalar regressors
		\end{itemize}
		\vspace{0.2cm}

		Coefficients can then be estimated using theory from \textbf{multivariate regression} leading to an estimated coefficient vector $\hat{\psi}_L \in \mathbb{R}^L$.
	\end{frame}

@@

		$$\hat{\beta}_L(t) = \sum_{j = 1}^{L} \hat{\psi}_{L,j} b_j(t)$$
		\vspace{0.2cm}

		This is dependent on...
		\begin{itemize}
			\item The functional basis $(b_j(t))_{j \in \mathcal{I}}$ for the estimation of $\beta(t)$
			\item The truncation parameter $L$
			\item (The functional basis used to approximate the observations)
			\item (The truncation parameter in the approximation of the observations)
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Spectral Representation of Random Vectors}
		Let $X(\omega)$ be a random vector realizing in $\mathbb{R}^p$.

		\begin{itemize}
			\item Let $\mu_x = \mathbb{E}(X)$ and $\Sigma_X = Cov(X)$
			\item Let $\{\gamma_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\Sigma_X$
			\item Let $\{\lambda_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\Sigma_X$
		\end{itemize}

		\vspace{0.2cm}
		Then $X$ can also be represented as
		$$X(\omega) = \mu_x + \sum_{i = 1}^{p} \xi_i(\omega) \gamma_i$$
		where the $\xi_i(\omega)$ have the following properties

		\begin{multicols}{2}
			\begin{enumerate}
				\item $\mathbb{E}[\xi_i(\omega)] = 0$
				\item $Var(\xi_i(\omega)) = \lambda_i$
				\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
			\end{enumerate}
		\end{multicols}
	\end{frame}

@@

		\textbf{Mean Function}: $$\mu(t) = \mathbb{E}\left[ F(\omega)(t) \right]$$

		\textbf{Autocovariance Function}: $$c(t,s) = \mathbb{E}\big[ \left( F(\omega)(t) - \mu(t) \right) \left( F(\omega)(s) - \mu(s) \right) \big]$$

@@

	\begin{frame}{Karhunen-Lo\'{e}ve Expansion}
		A random function $F(\omega)$ can be expressed in terms of its mean function and its Eigenfunctions:
		$$F(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)$$

@@

		This representation is called the \textbf{Karhunen-Lo\'{e}ve Expansion} of the random function $F$ and the Eigenfunctions can serve as a basis to represent the function.
	\end{frame}

	\begin{frame}{Principal Component Analysis}
		A related concept is \textbf{Principal Component Analysis} (PCA).
		\vspace{0.2cm}

		$\Sigma_X$ unknown $\rightarrow$ \textbf{sample analogues}

		\begin{itemize}
			\item Let $\mathbf{X} \in \mathbb{R}^{n \times p}$ contain the standardized regressors
			\item Let $\hat{\Sigma}_X = \frac{\mathbf{X}'\mathbf{X}}{n}$
			\item Let $\{\hat{\gamma}_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\hat{\Sigma}_X$
			\item Let $\{\hat{\lambda}_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\hat{\Sigma}_X$
		\end{itemize}
		\vspace{0.2cm}

		Then $Z_i(\omega) = \hat{\gamma}_i' X(\omega)$ is called the i'th principal component and
		\begin{multicols}{2}
			\begin{enumerate}
				\item $\mathbb{E}[Z_i(\omega)] = 0$
				\item $Var(Z_i(\omega)) = \hat{\lambda}_i$
				\item $Cov(Z_i(\omega), Z_j(\omega)) = 0$ for $i \neq j$
			\end{enumerate}
		\end{multicols}
	\end{frame}

	\begin{frame}{Functional Principal Component Analysis}
		This idea can be extended to functional regressors in the form of \textbf{Functional Principal Component Analysis} (FPCA).
		\vspace{0.2cm}

@@

		$$\tilde{F}(\omega)(t) = \hat{\mu}(t) + \sum_{j = 1}^{\infty} \tilde{\xi}_j(\omega) \hat{\nu}_j(t)$$

@@

	\begin{frame}{Simulation Setup \& Application cont.}
		Let 
		$$Y_{1,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)$$ 
		$$Y_{2,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)$$

>>>>

% Title page details: 
\title{Scalar on Function Regression \\
with Applications to Near-Infrared Spectography}
\author{Jonathan Willnow, Jakob Juergens, Jonghun Baek}
\date{{\color{red}}Presentation Day}

@@

		\begin{itemize}
			\item \textbf{Near-Infrared} (NIR) \textbf{Spectroscopy} enables fast diagnostics by using the NIR region of the electromagnetic spectrum (from 780 nm to 2500 nm)
			\item Suited for field-monitoring / on-line analysis
			\item Spectroscopy results in high-dimensional dataset.	
			\item This set of measurements serves as set of discretized approximations of smooth spectral curves
			\item Regression to determine relationship between octane rating and spectral curves
			\end{itemize}
	\end{frame}

@@

	%\begin{frame}{Theory}
	%	Jonghun
	%	\begin{itemize}
	%		\item Random Functions (name square integrable functions)
	%		\item Motivate continuous stochastic processes (growth curves/electricity consumption/yield curves/stonks)
	%		\item Use curves to predict a scalar response (show typical dgp)
	%	\end{itemize}
	%\end{frame}

	%\begin{frame}{Theory}
	%	Jonghun
	%	\begin{itemize}
	%		\item Basis expansions (b-splines and fourier)
	%		\item Talk about purposes
	%		\item Plots and show bias variance tradeoff
	%	\end{itemize}
	%\end{frame}

	\begin{frame}{Random Function}
		A \textbf{Random Variable} is a function $X : \Omega \rightarrow \mathcal{S}$ which is defined on a common probability space $(\Omega, \mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a $\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}.$
		\begin{itemize}
			\item If $\mathcal{S} = \mathbb{R}$ then $X$ is a random variable
			\item If $\mathcal{S} = \mathbb{R}^{n}$ then $X$ is a random vector
			\item If $\mathcal{S}$ is a space of functions, $X$ is called a \textbf{Random Function}
		\end{itemize}
	\end{frame}

	\begin{frame}{Random Function}
		Let $\mathbb{E}$ be the index set and this can be described as
		$${\{X(t,\omega) : t \in \mathbb{E}, \omega \in \Omega\},}$$
		where $X(t, \cdot)$ is $\mathcal{F}$-measurable function on the sample space $\Omega$.\\
		\begin{itemize}
			\item It can be shortened to $X(t)$ by omitting $\omega$
			\item The function is realized when the $X(t)$ exists $\forall t \in \mathbb{E}$
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Square Integrable Function}
		If a function $f(t)$ satisfies:
		$$\int_{0}^{1} \{f(t)\}^{2}dt < \infty$$
		the function $f$ is called \textbf{Square Integrable Function}\\
		and in the set $\mathbb{L}^{2}[0,1]$.
		\begin{itemize}
			\item Without loss of generality, the interval is defined in $[0,1] $
			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
			\item We focus on $\mathbb{L}^{2} [0,1]$ since the domain of our function is on the real line.
		\end{itemize}
	\end{frame}

	\begin{frame}{Square Integrable Function}
		Let $f, g \in \mathbb{L}^{2}[0,1]$, then
		%$$(ab + bg)(t) = af(t) + bg(t), \quad t \in [0,1] and \forall a,b$$
		%, where $a$ and $b$ are scalars. (Maybe don't need)\\
		%We can additionally define the inner product as follows:
		$$\langle f,g \rangle = \int_{0}^{1} f(t)g(t)dt$$
		%\begin{itemize}
		%	\item 
		Orthogonality of two different functions $\langle f,g \rangle = 0$
			%\item Distance between functions
		%\end{itemize}
	\end{frame}

	%\begin{frame}{Stochastic Process Perspective}
	%	Functional data are the sample curves observed from continuous time stochastic precess.\\
	%	\begin{itemize}
	%		\item From this perspective, $X(t)$ is a random variable (?)\\
	%		\item $X(\cdot)$ is a collection of random variables by each time index(?)\\
	%		\item Realizations of a random function belong in large collection of functions
	%	\end{itemize}		
	%\end{frame}

	\begin{frame}{Basis Expansion}
		\textbf{Basis Expansion} is a linear combination of functions defining a function as described:
		$$X_{i}(t) = \sum_{k=1}^{\infty} c_{ik}\phi_{k}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad i = 1, \dots, n, \quad \forall t \in \mathbb{E}$$
		where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient. We truncate the basis at $K$ to:
		\vspace{0.2cm}

		\begin{itemize}
			\item make the function smoother
			\item replace the original curves $X_{i}(t)$ by a smaller collection of $c_{nm}$
			%\item replace the original scalar data $X_{n}(t_{jn})$ by a smaller collection of $c_{nm}$
		\end{itemize}		
	\end{frame}

	\begin{frame}{Two Typical Types of Basis Function}
		\textbf{Fourier Basis Function} is written as
		$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\
		\vspace{2\baselineskip}
		\textbf{B-spline Basis Function} is a flexible curve defined by degree and knots. \\
		Each B-spline basis function, $i$-th B-spline basis function of degree $p$, $N_{i,p}(u)$ is defined on Cox-de Boor recursion formula.
	\end{frame}

@@

	\begin{frame}{Trade Off between Bias and Variance}
		How do we choose the number $K$ of basis functions?
		$$\textbf{MSE}[\hat{x}(t)] = \textbf{Bias}^2[\hat{x}(t)] + \textbf{Var}[\hat{x}(t)]$$

		{\color{red} Integrated Mean Squared Error}
		\begin{itemize}
			\item The larger $K$, the better fit to the data with also fitting noise
			\item If $K$ is too small, it would miss some significant information that we want to estimate 
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Estimation via Basis Representation}
		Assume the following \textbf{Data Generating Process}
		$$Y(\omega) = \alpha + \int_{0}^{1} \beta(s) X(\omega)(s) \mathrm{d}s + \epsilon(\omega)$$
		\vspace{-0.6cm}
		\begin{itemize}
			\item $Y(\omega)$ and $\epsilon(\omega)$ realize in $\mathbb{R}$ and $X(\omega)$ realizes in $\mathbb{L}^2[0,1]$
		\end{itemize}
		\vspace{0.3cm}

		Let $\{\phi_i(t) \: \vert \: i = 1, \dots, \infty\}$ be a basis of $\mathbb{L}^2[0,1]$ leading to the following representation of $\beta(t)$

		$$\beta(t) = \sum_{j = 1}^{\infty} c_j \phi_j(t) \approx \sum_{j = 1}^{L} c_j b_j(t)$$
		%Assume that we have a data set containing observations each of which is made up of:
		%\begin{itemize}
		%	\item $y_i$: a scalar realization of $Y(\omega)$ - the octane rating of gasoline
		%	\item $x_i(t)$: a realization of $X(\omega)$ - the measured NIR spectrum
		%\end{itemize}

@@

	\begin{frame}{Estimation via Basis Representation}
		We can transform the data generating process into:
		\begin{equation}\notag
			\begin{split}
				Y(\omega) & = \alpha + \int_{0}^{1}\left[\left(\sum_{j = 1}^{\infty} c_j  \phi_j(s)\right) X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
						  & = \alpha + \sum_{j = 1}^{\infty} \left[c_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)	 \\
						  & = \alpha + \sum_{j = 1}^{\infty} c_j {\color{red}Z_j(\omega)} + \epsilon(\omega)  
			\end{split}
		\end{equation}

		Where a $Z_j(\omega)$ is a \textbf{scalar random variable}.
	\end{frame}

	\begin{frame}{Estimation via Basis Representation}
		Each combination of $x_i(t)$ and $\phi_j(t)$ gives us
		$$Z_{i,j} = \int_{0}^{1} x_i(s) b_j(s)\mathrm{d}s$$

		\begin{itemize}
			\item This allows us to write each observation in the data set as $\{y_i, Z_{i,1}, Z_{i,2}, \dots\}$
			\item Truncating the functional basis yields an approximation $\{y_i, Z_{i,1}, Z_{i,2}, \dots, Z_{i,L}\}$
		\end{itemize}

		Coefficients can then be estimated using theory from \textbf{multivariate regression} leading to an estimated coefficient vector $\hat{c} \in \mathbb{R}^L$.
	\end{frame}

@@

		$$\hat{\beta}_L(t) = \sum_{j = 1}^{L} \hat{c}_{L,j} \phi_j(t)$$

		This is dependent on...
		\begin{itemize}
			\item The basis $(\phi_j(t))_{j \in \mathcal{I}}$ for the estimation of $\beta(t)$
			\item The truncation parameter $L$
			\item The basis $(\psi_j(t))_{j \in \mathcal{I}}$ used for the expansion of the observations
			\item The truncation parameter in the approximation of the observations $K$
		\end{itemize}
	\end{frame}

@@

	%\begin{frame}{Spectral Representation of Random Vectors}
	%	Let $X(\omega)$ be a random vector realizing in $\mathbb{R}^p$.

	%	\begin{itemize}
	%		\item Let $\mu_x = \mathbb{E}(X)$ and $\Sigma_X = Cov(X)$
	%		\item Let $\{\gamma_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\Sigma_X$
	%		\item Let $\{\lambda_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\Sigma_X$
	%	\end{itemize}

	%	\vspace{0.2cm}
	%	Then $X$ can also be represented as
	%	$$X(\omega) = \mu_x + \sum_{i = 1}^{p} \xi_i(\omega) \gamma_i$$
	%	where the $\xi_i(\omega)$ have the following properties

	%	\begin{multicols}{2}
	%		\begin{enumerate}
	%			\item $\mathbb{E}[\xi_i(\omega)] = 0$
	%			\item $Var(\xi_i(\omega)) = \lambda_i$
	%			\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
	%		\end{enumerate}
	%	\end{multicols}
	%\end{frame}

@@

		\textbf{Mean Function}: $$\mu(t) = \mathbb{E}\left[ X(\omega)(t) \right]$$

		\textbf{Autocovariance Function}: $$c(t,s) = \mathbb{E}\big[ \left( X(\omega)(t) - \mu(t) \right) \left( X(\omega)(s) - \mu(s) \right) \big]$$

@@

	\begin{frame}{Karhunen-Lo\'{e}ve Expansion}
		A random function $X(\omega)$ can be expressed in terms of its mean function and its Eigenfunctions:
		$$X(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)$$

@@

		This is called the \textbf{Karhunen-Lo\'{e}ve Expansion} of $X(\omega)$ and the Eigenfunctions can serve as a basis.
	\end{frame}

	%\begin{frame}{Principal Component Analysis}
	%	A related concept is \textbf{Principal Component Analysis} (PCA).
	%	\vspace{0.2cm}
	%	
	%	$\Sigma_X$ unknown $\rightarrow$ \textbf{sample analogues}
	%
	%	\begin{itemize}
	%		\item Let $\mathbf{X} \in \mathbb{R}^{n \times p}$ contain the standardized regressors
	%		\item Let $\hat{\Sigma}_X = \frac{\mathbf{X}'\mathbf{X}}{n}$
	%		\item Let $\{\hat{\gamma}_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\hat{\Sigma}_X$
	%		\item Let $\{\hat{\lambda}_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\hat{\Sigma}_X$
	%	\end{itemize}
	%	\vspace{0.2cm}

	%	Then $Z_i(\omega) = \hat{\gamma}_i' X(\omega)$ is called the i'th principal component and
	%	\begin{multicols}{2}
	%		\begin{enumerate}
	%			\item $\mathbb{E}[Z_i(\omega)] = 0$
	%			\item $Var(Z_i(\omega)) = \hat{\lambda}_i$
	%			\item $Cov(Z_i(\omega), Z_j(\omega)) = 0$ for $i \neq j$
	%		\end{enumerate}
	%	\end{multicols}
	%\end{frame}

	\begin{frame}{Functional Principal Component Analysis}
		{\color{red} Rephrase this!} This idea can be extended to functional regressors in the form of \textbf{Functional Principal Component Analysis} (FPCA).
		\vspace{0.2cm}

@@

		$$\tilde{F}(\omega)(t) = \hat{\mu}(t) + \sum_{j = 1}^{J} \tilde{\xi}_j(\omega) \hat{\nu}_j(t)$$

@@

	\begin{frame}{Simulation Setup \& Application cont.}
		Let 
		$$Y_{1,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.9} - var(\langle NIR, f\rangle)$$ 
		$$Y_{2,f} = \langle NIR, f\rangle + Z  \frac{var(\langle NIR, f\rangle)}{0.6} - var(\langle NIR, f\rangle)$$
